---
output: github_document
---

[![Travis build status](https://travis-ci.org/USCbiostats/sluRm.svg?branch=master)](https://travis-ci.org/USCbiostats/sluRm)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
options(width = 80)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# sluRm

Example

```{r simple-example}
library(sluRm)

# Suppose that we have 100 vectors of length 50 ~ Unif(0,1)
set.seed(881)
x <- replicate(100, runif(50))
```

We can use the function `Slurm_lapply` to distribute computations

```{r}
ans <- Slurm_lapply(x, mean, submit = FALSE)
```

Notice the `submit = FALSE` option. To get more info, we can actually set the verbose mode on

```{r}
opts_sluRm$verbose_on()
ans <- Slurm_lapply(x, mean, submit = FALSE)
```


Take a look at the vignette [here](vignettes/getting-started.Rmd).

## Installation


And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("USCbiostats/sluRm")
```
## Example

This is a basic example which shows you how to solve a common problem:

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

## Contributing

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
