---
output: github_document
---

[![Travis build status](https://travis-ci.org/USCbiostats/sluRm.svg?branch=master)](https://travis-ci.org/USCbiostats/sluRm)
[![codecov](https://codecov.io/gh/USCbiostats/sluRm/branch/master/graph/badge.svg)](https://codecov.io/gh/USCbiostats/sluRm)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
options(width = 80)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# sluRm: A lightweight wrapper for Slurm <img src="man/figures/logo.svg" height="180px" align="right"/>

Slurm Workload Manager is a popular HPC cluster job scheduler found in many of the top 500 super computers. The `sluRm` R package provides an R wrapper to it that matches the parallel package's syntax, this is, just like `parallel` provides the `parLapply`, `parMap`, `parSapply`, etc., `sluRm` provides `Slurm_lapply`, `Slurm_Map`, `Slurm_sapply`, etc.

While there are other alternatives such as `future.batchtools` and `rslurm`, this R package has the following advantages over the other two:

1.  It is dependency free, which means that it works out-of-the-box

2.  Puts an emphasis on been similar to the workflow in the R package `parallel`

3.  It provides a general framework for the user to create its own wrappers without using template files.

## Installation


And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("USCbiostats/sluRm")
```

## Examples

```{r simple-example}
library(sluRm)

# Suppose that we have 100 vectors of length 50 ~ Unif(0,1)
set.seed(881)
x <- replicate(100, runif(50))
```

We can use the function `Slurm_lapply` to distribute computations

```{r}
ans <- Slurm_lapply(x, mean, submit = FALSE)
```

Notice the `submit = FALSE` option. To get more info, we can actually set the verbose mode on

```{r}
opts_sluRm$verbose_on()
ans <- Slurm_lapply(x, mean, submit = FALSE)
```


Take a look at the vignette [here](vignettes/getting-started.Rmd).


## Contributing

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

## Funding

Supported by National Cancer Institute Grant #1P01CA196596.
